---
title: "Peer-graded Assignment: R Markdown and Leaflet"
author: "Patricia Ortiz Suárez"
date: "September 16, 2017"
output: html_document
---

##Instructions

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

##Assignement

###Assignement Date: `r Sys.Date()`

```{r echo = FALSE, warning=FALSE}
suppressMessages(library(dplyr))
suppressMessages(library(leaflet))
suppressMessages(library(knitr))

df <- read.csv("simplemaps-worldcities-basic.csv")
df <- df %>% filter(country == "Dominican Republic") %>% select(city,lat,lng,pop,country)

```

###Data

The data that was used for this map was obtained from simplemaps.com
I used the [World Cities Database](http://simplemaps.com/data/world-cities) that can be downloaded from [here](http://simplemaps.com/data/world-cities) and created a sub-set for my country, The Dominican Republic.

Here is the data:

```{r echo =FALSE, comment=""}
kable(df)
```

###Map

Here is the map:

```{r echo=FALSE}
df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(df$pop) * 30)

```
